TODO:Update
\def\eprintsmallskip{\smallskip}{}%
We introduce a new cryptographic primitive, named
 \emph{ring verifiable random functions (ring VRF)},
 which provides an array of uses, especially in anonymous credentials.
% Anonymized
%\eprint{Ring VRFs are}{We introduce ring VRFs, which are}
Ring VRFs are ring signatures that prove correct evaluation
of an authorized signer's pseudoramdom function, while hiding the signer's
identity within some set of possible signers.

We present a family of ring VRF protocols with surprisingly efficient
instantiations, due to our novel {\em zero-knowledge continuation} technique.
Intuitively our ring VRF signers generate two linked proofs, an inexpensive
 one for PRF evaluation and one for ring membership, which can be reused. 
%An evaluation proof needs only a cheap Chaum-Pedersen DLEQ proof.
%, while ring membership proof depends only upon the ring itself.
We reuse the ring membership proof across multiple inputs
by expanding a Groth16 trusted setup to re-hide public inputs when
 rerandomizing the Groth16, ensuring that these reuses of the same proof are unlinkable.
Our fastest amortized ring VRF needs only eight $\mathcal{G}_1$
 and two $\mathcal{G}_2$ scalar multiplications, 
making it the only ring signature with performance competitive with group signatures.

\eprintsmallskip

A ring VRF can be used to obtain a unique pseudo-anonymous identity from a given a list of identities.
By using a different input for the ring VRF in different contexts, we can generate a pseudonym for each context that is unlinkable between different contexts. We discuss applications that range across the anonymous credential space.

%We discuss applications that range across the anonymous credential space:As in proof-of-personhood work by  Bryan Ford, et al., a ring VRF output acts like a unique pseudo-anonymous identity within some desired context, given as the ring VRF input, but remains unlinkable between different contexts. These unlinkable but unique pseudonyms provide a better balance between user privacy and service provider or social interests than attribute based credentials like IRMA (``I Reveal My Attributes'') credentials.

%\eprintsmallskip
%Ring VRFs support anonymously rationing or rate limiting resource
%consumption that winds up vastly more flexible and efficient than
%purchases via money-like protocols.

\eprintsmallskip
We define the security of ring VRFs in the universally composable (UC) model and show that our protocol is UC secure.
