
\subsection{Safer}

\newcommand\pijub{\ensuremath{\pi_{\mathtt{jub}}}\xspace}
\newcommand\pijubdot{\ensuremath{\dot{\pi}_{\mathtt{jub}}}\xspace}


Although blindingly fast, we processed $\sk$ directly inside $\pifast$,
which annoys those wanting lightweight HSM provers, and
increases side channel attack risks.

We could easily build a safer circuit in which
\PedVRF runs on, and $\pk$ lies in, the Jubjub curve $\ecJ$, like 
$$ \pisafe = \rrSNARK \Setst{ \pk, \comring }{
 \exists \openring \textrm{\ s.t.\ }
 \pk = \rVRF.\OpenKey(\comring,\openring)
} \mathperiod $$
In this, our $\genG$ and $\genB$ have no relation with $\ecE$
or \pisafe, so now our $X'$ nolonger plays nicely with \PedVRF, 
$$ X' = \comring\, Y_0 + \pk.x Y_1 + \pk.y Y_2 + b \genB_\gamma \mathperiod $$

Instead we propose a small second SNARK $\pisafedot'$ working on $\ecE$
with two tasks, strip the blinding $b \genB_\gamma \in \ecE$ needed
by our zero-knowledge continuation, and then adding the Pedersen blinding
in $\ecJ$ required by \PedVRF, ala
 $\compk = \PedVRF.\CommitKey(\compk,\openpk) = \pk + \openpk \genB \in \ecJ$.
We create $\pisafedot'$ by again applying our opaque Pedersen input trick to
$$ \pisafedot = \rrSNARK \Setst{ \compk, \pk }{
 \exists \openpk \textrm{\ s.t.\ } \compk = \pk + \openpk \genB
} \mathperiod $$

As $\pisafedot$ knows the $\openpk$ of \PedVRF,
$\pisafedot$ cannot be another zero-knowledge continuation itself.
As $\pisafedot$ does not require rerandomization, another SNARK besides
Groth16 \cite{Groth16} works here, perhaps like Plonk \cite{plonk} or
some inner product proof \cite{bootle,bulletproofs},
 assuming the opaque Pedersen input trick works.

Assuming we use Groth16 \cite{Groth16} for $\pisafedot$,
our SRS needs a fresh $\dot{\delta}$ but one could take
$\dot{\gamma} = \gamma$ if so desired \cite{???}, and anyways
$\genB_{\dot{\gamma}} = \genB_{\gamma}$.
At this point our verifier supplies transperent public inputs
 $\compk.x \dot{Y}_1 + \compk.y \dot{Y}_2$ and uses opaque inputs
$$ \dot{Y} = \dot{X}' - \compk.x \dot{Y}_1 + \compk.y \dot{Y}_2 =
- \pk.x \dot{Y}_3 + \pk.y \dot{Y}_4 + b \genB_{\dot{\gamma}} \mathperiod $$

In this, we nolonger prove knowledge of $X$ in \PedVRF like $\pifast$ did.
Instead, we employ another Chaum-Pedersen DLEQ proof $\dot{\sigma}$ to wire
 the $X'$ of $\pisafe$ to the $\dot{X}'$ of $\pisafedot$,
 thus proving knowledge of both.
We cannot avoid this proof-of-knowledge, but it becomes simpler if
we choose $Y'_3 = Y_1$ and $Y'_4 = Y_2$ using the trick of \S\ref{sec:ring_hiding}.

We take $\aux \doubleplus \pisafe \doubleplus \pisafedot
 \doubleplus \dot{\sigma} \doubleplus \dot{Y}$
 to be the \aux of \PedVRF of course.

\begin{proposition}\label{prop:pisafe_anonymity}
\rVRF using \pisafe satisfies ring anonymity.
\end{proposition}

\begin{proof}[Proof stetch.]
???
\end{proof}

% \smallskip

As \openpk appears inside $\pisafedot$, we recompute $\pisafedot$ with
every ring VRF signature, but the elliptic curve addition requires
only 5ish constraints, and the elliptic curve scalar multiplication
requires under 750 ??? constraints. 
All told our amortized prover runs faster than a Groth16 prover
with 800 constraints.

A priori, our safer verifier requires five pairings, along with
some additional $\ecE_1$ scalar multiplications.
We conjecture $\gamma$ and $\delta$ could safely be shared between
$\pisafe$ and $\pisafedot$, thereby requiring only four pairings,
but caution this result appars non-trivial.

% \smallskip


