\section{Application: Identity}
\label{sec:app_identity}

Ring VRFs yield anonymous identity systems:
After a user and service establish a secure channel and
the server authenticates itself with certificates, then
the user authenticates themselves by providing an anonymous
VRF signature with input \msg being the service's identity,
thus creating an pseudonymous identified session with
a pseudonym unlinkable from other contexts.

We expand this identified session workflow with an extra
update operation suitable for our ring VRF's amortized prover.
We discuss only \pifast here but all techniques apply to \pisk and \pipk similarly. 

\begin{itemize}
\item {\em Register} --
 Adds users' public key commitments into some \ring,
 after verifying the user does not currently exist in \ring.
\item {\em Update} --
 User agents regenerate their stored SNARK $(\pk,\pifast^\inner)$ using
 $\SpecialG.\Preprove( (\sk_1,\sk_2,\openring); (\sk,\comring) )$
 each time \ring changes, perhaps even receiving \comring and \openring
 from some ring management service.
\item {\em Identify} --
 Our user agent first opens a standard TLS connection to a server \msg,
 both checking the server's name is \msg and checking certificate
 transparency logs, and then computes the shared session id \aux.
 Our user agent computes the user's identity
  $\mathtt{id} = \PedVRF.\Eval(\sk,\msg)$ on the server id \msg,
 Our user agent next rerandomizes \pifast, \compk, and \openpk using
 $\SpecialG.\Reprove( \pk, \pifast^\inner )$, computes
  $\sigma = \PedVRF.\Sign(\sk,\openpk,\msg,\aux \doubleplus \compk \doubleplus \pifast)$,
 and finally sends the server their ring VRF signature $(\compk,\pifast,\sigma)$
 % $\rVRF.\rSign(\sk,\openring,\msg,\aux)$ % $ = (\compk,\pifast,\sigma)$.
\item {\em Verify} -- 
 After receiving $(\compk,\pifast,\sigma)$ in channel \aux,
 the server named \msg checks $\SpecialG.\Verify( \comring, (\compk,\pifast) )$,
 checks the VRF signature, and obtains the user's identity $\mathtt{id}$, ala \\
 $\mathtt{id} = \PedVRF.\Verify(\compk,\msg,\aux \doubleplus \compk \doubleplus \pifast,\sigma)$.
\end{itemize}


\subsection{Browsers}

We must not link users' identities at different web sites, so user agents
should carefully limit cross site resource loading, referrer information, etc.
User agents could always load purely static resources, without metadata
like cookies or referrer information.
% especially purely content addressable resources.
At least Tor browser already takes cross site resource concerns seriously,
while Safari and Brave may limit invasive cross site resources too.
% In any case, one could always specify rules against cross site privacy invasions
% whenever writing ring VRF browser specifications.

We somewhat trust the CAs and CT log system with users' identities in
the above protocol, in that users could login to a site with fraudulent
credentials.  We think cross site restrictions limit this attack vector.
If stronger defenses are desired then instead of \msg being the site name,
\msg could be a public ``root'' key for the specific site, which then
also certifies its TLS certificate.  Ideally its secret key remains air gaped.


\subsection{AML/KYC}
\label{subsec:AML_KYC}

We shall not discuss AML/KYC in detail, because the entire field lacks
clear goals, and thus winds up being ineffective
 \cite{doi:10.1080/25741292.2020.1725366}.
% https://www.tandfonline.com/doi/full/10.1080/25741292.2020.1725366
% via https://twitter.com/ronaldpol/status/1491548352189587460
We do however observe that AML/KYC typically conflicts with security
and privacy laws like GDPR.  As a compromise between these regulations,
one needs a compliance party who know users' identities,
 while another separate service party knows the users' activities.
We propose a safer and more efficient solution:

Instead our compliance party becomes an identity issuer who maintains
a public \ring, and privately knows the users behind each public key.
As above, identity systems could employ \ring freely for diverse purposes.
If later asked or subpoenaed, users could prove their relevant identities
to investigators, or maybe prove which services they use and do not use. 

Interestingly \PedVRF could run ``backwards'' like
 $H_{\grE'}(\msg) \ne \sk^{-1} \, \PreOut$
to show a ring VRF output associated to $\PreOut$
does not belong to the user, without revealing the users'
identity $\Hout(\msg, \sk \, H_{\grE'}(\msg))$ to investigators. 

Our applications mostly ignore key multiplicity. 
AML/KYC demands suspects prove non-involvement using ring VRFs.

\begin{definition}\label{def:rvrf_exculpability}
We say \rVRF is {\em exculpatory} if we have an efficient algorithm
for equivalence of public keys, but a PPT adversary \adv cannot
find non-equivalent public keys $\pk_0,\pk_1$ with colliding VRF outputs.
% (perfectly or computationally)
% (either ever or with advantage negligible advantage in $\secparam$)
\end{definition}

A priori, our JubJub representations $\sk_0 \genJ_0 + \sk_1 \genJ_1$
used in \S\ref{subsec:rvrf_faster} and \S\ref{subsec:rvrf_side_channel}
costs us exculpability from Definition \ref{def:rvrf_exculpability}.
% Ad hoc rings ...
% Rings used for AML/KYC would be maintained by an authority and require
% some registration procedure, using government issued identity documents.

There is however a natural {\em exculpable public key} flavor $(\pk,\sigma)$,
in which
 $\sigma = \Sign(\sk, \CommitRing(\{ \pk \},\pk).\openring, \mathtt{ring\_name}, \mathtt{""})$.
The singleton ring $\{ \pk \}$ ensure that 
$\rVerify(\CommitRing(\{\pk\}), \mathtt{ring\_name}, \mathtt{""}, \sigma)$
uniquely determines the secret key, so exculpability holds
 if joining the ring requires $(\pk,\sigma)$.

% \begin{proposition}
% \end{proposition}


\subsection{Moderation}
\label{subsec:moderation}

All discussion or collaboration sites have behavioral guidelines and
moderation rules that deeply impact their culture and collective values.

Our ring VRFs enables a simple blacklisting operation:
If a user misbehaves, then sites could blacklist or otherwise penalizes
their site local identity $\mathtt{id}$.
As $\mathtt{id}$ remains unlinked from other sites, we avoid thorny
questions about how such penalties impact the user elsewhere, and thus
can assess and dispense justice more precisely. 

At the same time, there exist sites who must forget users' histories
eventually, like under some ``right to be forgotten'' principle, either
GDPR compliance or an ethical principle of social mistakes being ephemeral.

We obtain ephemeral identities if \msg consists of the site name plus
the current year and month, or some other approximate date.
In this way, users have only one stable $\mathtt{id}$ within the
approximate date range, but they obtain fresh $\mathtt{id}$s merely
by waiting until the next month.

We could adjust \PedVRF to simultaneously prove multiple VRF input-output
pairs $(\msg_j,\mathtt{id}_j)$.
As in \cite{PrivacyPass}, we merely delinearize \In and \PreOut in
\rSign and \rVerify like:
\begin{align*}
x &= H(\msg_j,\mathtt{id}_j,\ldots,\msg_j,\mathtt{id}_j) \\
\In &= \sum_j H_p(x,j) \, \In_j \\
\PreOut &= \sum_j H_p(x,j) \, \PreOut_j \\
\end{align*}

As doing so links these pairs together,
we could link together two or more ephemeral identities like this
to obtain a semi-permanent identity with user controlled revocation:
As login, our site demands two linked input-output pairs given by
 $\msg_1 = \mathtt{site\_name} \doubleplus \mathtt{current\_month}$ and
 $\msg_2 = \mathtt{site\_name} \doubleplus \mathtt{registration\_month}$,
so users could have multiple active pseudo-nyms given by $\mathtt{id}_2$,
but only one active pseudo-nym per month, enforced by deduplicating
 $\mathtt{id}_1$, which still prevents spam and abuse.

If instead our site associates pseudo-nyms to their most recently seen
$\mathtt{id}_1$, then we could link adjacent months, meaning $\msg_j$
is defined by the $j$th previous month, until reaching a previously used $\mathtt{id}_1$.
In this model, pseudo-nyms could be abandoned and replaced, but
abandoned pseudo-nyms cannot then be reclaimed without linking intervening dates.
Although more costly, sites could permanently bans a few problematic
users via the inequality proofs described in \S\ref{subsec:AML_KYC} too.

In these ways, sites encode important aspects of their moderation rules
into the ring VRF inputs they demand.  
% We expect this makes sites' values and culture more uniform, predictable, and transparent.


\subsection{Reduced pairings}
\label{sec:reduced_pairings}

At a high level, we distinguish moderation-like applications discussed
above, which resemble classic identity applications like AML/KYC, from
rate limiting applications discussed in the next section. 
%
In moderation-like applications, ring VRF outputs become long-term
stable identities, so users typically reidentify themselves many times
to the same sites, reusing the exact same \msg.

As an optimization, our zero-knowledge continuation could reuse the
same \compk and \pifast for the same \msg, so that verifiers could
memoize their verifications of \pifast.  We spend most verifier time
checking the Groth16 pairing equation, so this saves considerable CPU time. % assuming our cache wind up fast enough.

As a concrete example, our coefficients $r_1,r_2,b$ used for
rerandomization in \S\ref{sec:rvrf_cont} could be chosen
deterministically like $r_1,r_2,b \leftarrow H(\sk,\msg)$.
In this way, each (helpful) user's $\mathtt{id}$ has a unique \pifast,
which verifiers could memoize by storing
 $(\mathtt{id},H(\compk \doubleplus \pifast),\mathtt{dates})$
after their first verification, but then skipping the Groth16 check
 after merely rechecking the hash $H(\compk \doubleplus \pifast)$.

We could risk denial-of-service attacks by users who vary $r_1,r_2,b$ 
randomly however.  We therefore suggest $\mathtt{dates}$ record the last
several previous dates when $H(\compk \doubleplus \pifast)$ changed.
We rate limit or verify more lazily users with many nearby login dates

