\documentclass[runningheads,evcountsame,a4paper,11pt,orivec]{llncs}
\usepackage[margin=2.5cm,includefoot]{geometry}

%=================Begin:Packages===================
\usepackage{graphicx}
\usepackage{bmpsize}
\usepackage{algorithm}

\usepackage[noend]{algpseudocode}
% \usepackage{enumitem}
\usepackage{url}
%\usepackage{amsthm}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
% \usepackage[capitalize,nameinlink]{cleveref}
% \usepackage{framed}
% \usepackage{fancybox}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
% \usepackage{tcolorbox}
\usepackage{tikz}
% \usepackage{todonotes}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage[advantage,
adversary,
asymptotics,
complexity,
ff,
mm,
operators,
probability,
]{cryptocode}
\usepackage[linewidth=1pt]{mdframed}
\usepackage{ulem}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes}

% TODO: Clean up macros
\input{macros/style.tex}
\input{macros/primitives.tex}
\input{macros/other.tex}


\sloppy


\title{Ethical identity, ring VRFs, and zero-knowledge continuations}

\author{Jeffrey Burdges \and Handan Kilinc-Alper \and Alistair Stewart \and Sergey Vasilyev}
\date{}
\institute{Web 3.0 Foundation}


\begin{document}
	
\maketitle

\begin{abstract}
Verifiable random functions (VRFs) weld a pseudorandom function (PRF) into
a signature scheme, so that valid signatures prove correct PRF evaluations.
VRFs have diverse applications in consensus protocols like randomness
beacons, DNS via NSEC5, certificate transparency, and online games.

Anonymized {\em ring VRFs} are then ring signatures that similarly prove
correct evaluation of some authorized signer's PRF while hiding the
specific signer's identity.
Ring VRFs integrate with distributed systems better, and provide more robust
anonymity, than similar schemes like group VRFs or threshold protocols.

% Above unecessary in the abstract?

We propose ring VRFs as a natural fulcrum around which a diverse array of
zkSNARK circuits turn, which thus makes ring VRFs an ideal target
for optimization and eventually standards. 

%

Among their diverse uses, we focus upon identity-like cases in which
ring VRF outputs act like pseudonyms provably unique within some context,
 specified via the VRF input, but unlinkable between contexts. 
These unlinkabile but unique pseudonyms provide an excellent balance between
user privacy and service provider or social interests \cite{pop2008}.
%
In fact, identity systems without unlinkability like OAuth wind up being
unethical when used outside specific narrow relationships.
% TODO: ``one person, one persona'' \cite{pop2008} https://bford.info/pub/net/sybil.pdf

%

As our core optimization tool, we explore {\em zero-knowledge continuations}
of rerandomizable zkSNARKs like \cite{groth16} to amortize expensive
ring membership proofs across many ring VRF outputs. 
%
We implement a broadly usable ring VRF that amortizes an arbitrary
ring membership proofs, with a marginal prover cost
 of eight $\ecE_1$ and two $\ecE_2$ scalar multiplications.

In other words, our ring VRF might be first ring signature with asymptotic
performance compeditive with group sigantures.
%
We expect zero-knowledge continuations of rerandomizable zkSNARKs
thuroughly trounce recusive zkSNARK techniques indefinitely.
\end{abstract}


\input{intro}
% \input{identity}
\input{primitives}
\input{vrf_def}
\input{vrf_thin}
\input{vrf_pedersen}
\input{rvrf_def}
\input{rvrf_inst}
\input{app_id}




\bibliographystyle{plain}
\bibliography{refs_misc,refs_new,refs_sass}


\end{document}





\endinput




\newpage
MERGER IN PROGRESS
\newpage


\input{uc/model}
\input{uc/rvrf}

\input{uc/rvrf_se}	



